Irt plot extra

### 2023-11-05 manuscript_SciRep.Rmd
psych::describeBy code correction

mi.des.sum <- mi.descriptives %>% 
psych::describeBy("English_Speaking")

mi.english.sum <- english.speaking %>% 
psych::describeBy("slypos_demographics_sex.factor")

mi.non.english.sum <- non.english.speaking %>% 
psych::describeBy("slypos_demographics_sex.factor")

>>>>

mi.des.sum <- psych::describeBy(mi.descriptives ~ English_Speaking)

mi.english.sum <- psych::describeBy(english.speaking ~ slypos_demographics_sex.factor)

mi.non.english.sum <- psych::describeBy(non.english.speaking %>% slypos_demographics_sex.factor)
